\protect Connecting every bit of knowledge: \\ The structure of Wikipedia's First Link Network

### 2016-11-21 writeup/2016-04wikipedia-network/correspondence/2016-11-06-compsci-reviewers/2016-11-06-response.body.tex
updated response to reviewers

(a) Included pseudo-code for the traversal funnels algorithm as well as a description of the runtime and auxiliary memory usage in section B. Traversal Funnels. We have also made all code used for this work available in the online appendix.

>>>>

(a) Included pseudo-code for the traversal funnels algorithm as well as a description of the runtime and auxiliary memory usage in section B (Traversal Funnels). We have also made all code used in this work available on the online appendix.
